Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-18 WSSSPE2_report/WSSSPE2_review.tex
Add dates.

\author{TBD by contributions}
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,
%Richard Littauer$^{(9)}$,
%Miguel de Val-Borro$^{(10)}$, 
%Sou-Cheng T. Choi$^{(11)}$}
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}

\begin{abstract}
This technical report discusses the submission and peer-review process used by
the Second Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE2) and the results of that process. It is intended to record
both the alternative submission and program organization model used by WSSSPE2
as well as the papers associated with the workshop that resulted from that
process.
\end{abstract}

>>>>

\author{TBD by contributions \\{\scriptsize\today \quad  (Due:  $\backsim$ April 1)}}
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,
%Richard Littauer$^{(9)}$,
%Miguel de Val-Borro$^{(10)}$, 
%Sou-Cheng T. Choi$^{(11)}$}
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}

\begin{abstract} \todo{TBD due date above}       
This technical report discusses the submission and peer-review process used by
the Second Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE2) and the results of that process. It is intended to record
both the alternative submission and program organization model used by WSSSPE2
as well as the papers associated with the workshop that resulted from that
process.
\end{abstract}
